\textbf{Response Letter}

### 2018-12-22 doc/aij18/major-revision/aij18.tex
Sections 1 and 2 updated
Added answers related to section 6 to the letter

\newcommand{\ARMS}{{\small {\sffamily ARMS}}\xspace}
\newcommand{\CAMA}{{\small {\sffamily CAMA}}\xspace}
\newcommand{\SLAF}{{\small {\sffamily SLAF}}\xspace}
\newcommand{\LAMP}{{\small {\sffamily LAMP}}\xspace}
\newcommand{\NOISTA}{{\small {\sffamily NOISTA}}\xspace}
\newcommand{\LOCM}{{\small {\sffamily LOCM}}\xspace}
\newcommand{\LOCMtwo}{{\small {\sffamily LOCM2}}\xspace}
\newcommand{\LOP}{{\small {\sffamily LOP}}\xspace}
\newcommand{\AMAN}{{\small {\sffamily AMAN}}\xspace}
\newcommand{\FAMA}{{\small {\sffamily FAMA}}\xspace}

@@

\input{introduction}
\input{background}
\input{motivation}
\input{learning_task}
\input{evaluation}
\input{experiments}

@@

In this paper we have presented \FAMA, an approach for learning \strips\ action models based on the compilation of the learning task into a planning task. The distinctive characteristic of \FAMA over other state-of-the-art approaches is its ability to learn from minimal input knowledge and, more particularly, from minimal observability plan traces with no observed actions and no observed intermediate states. By lightening the input constraints, \FAMA opens up the way for action model learning to operate on real-world problems, as opposite to current approaches where the heavy input restrictions have limited their applicability to synthetic benchmarks. Our approach is thus very well suited for learning action models in data-based applications where the only observable information is a possibly incomplete sequence of partially observed states.

>>>>

\newcommand{\ARMS}{{\small {\sffamily ARMS}}\xspace}
\newcommand{\CAMA}{{\small {\sffamily CAMA}}\xspace}
\newcommand{\SLAF}{{\small {\sffamily SLAF}}\xspace}
\newcommand{\LAMP}{{\small {\sffamily LAMP}}\xspace}
\newcommand{\NOISTA}{{\small {\sffamily NOISTA}}\xspace}
\newcommand{\LOCM}{{\small {\sffamily LOCM}}\xspace}
\newcommand{\LOCMtwo}{{\small {\sffamily LOCM2}}\xspace}
\newcommand{\LOP}{{\small {\sffamily LOP}}\xspace}
\newcommand{\AMAN}{{\small {\sffamily AMAN}}\xspace}
\newcommand{\LOUGA}{{\small {\sffamily LOUGA}}\xspace}
\newcommand{\FAMA}{{\small {\sffamily FAMA}}\xspace}

@@

\input{introduction}
\input{background}
%\input{motivation}
\input{learning_task_def}
\input{learning_action_models}
\input{evaluation}
\input{experiments}

@@

In this paper we have presented \FAMA, an approach for learning \strips\ action models based on the compilation of the learning task into a planning task. The distinctive characteristic of \FAMA over other state-of-the-art approaches is its ability to learn from minimal input knowledge and, more particularly, from minimal observability plan traces with no observed actions and no observed intermediate states. By relaxing the input constraints, \FAMA opens up the way for action model learning to operate on real-world problems, as opposite to current approaches where the heavy input restrictions have limited their applicability to synthetic benchmarks. Our approach is thus very well suited for learning action models in data-based applications where the only observable information is a possibly incomplete sequence of partially observed states.

### 2018-12-22 doc/aij18/major-revision/experiments.tex
Added answers related to section 6 to the letter

This experiment evaluates the impact of $\left|\mathcal{T}\right|$, the size of the input knowledge, in the performance of \FAMA in order to:

@@

Figure~\ref{fig:pspace_quality} displays \textcolor{red}{the average precision and recall of the 15 learned models} in the scenario with unknown plan horizon. As expected, the quality of the learned models is lower than when the horizon of the plan is known. We can also observe in Figure~\ref{fig:pspace_quality} the opposite behaviour to Figure~\ref{fig:np_quality}; that is, we find a drop of the quality as the input knowledge increases. The drop in the score is caused by an increasing number of timeouts, meaning that no solution is found in many tasks within the given time-bound, and consequently a value of $0$ for precision and recall is assigned to these experiments. \textcolor{red}{The first timeout is found at $|\mathcal{T}| = 3$ in the \emph{grid} domain, and the number of timeouts increases until it reaches 6 with $|\mathcal{T}| = 10$.} Figure \ref{fig:pspace_time}, on the other hand, reflects that the computation time of the first case study is also higher than in the second case, which is explained by both the higher complexity and the large number of timeouts.

>>>>

This experiment evaluates the impact of $\left|\mathcal{T}\right|$, the size of the input knowledge, on the performance of \FAMA in order to:

@@

Figure~\ref{fig:pspace_quality} displays \textcolor{red}{the average precision and recall of the 15 learned models} in the scenario with unknown plan horizon. As expected, the quality of the learned models is lower than when the horizon of the plan is known. \textcolor{red}{The higher complexity of this setting is also reflected in the appearance of some timeouts when solving the learning task. The first timeout is found at $|\mathcal{T}| = 3$ in the \emph{grid} domain, and the number of timeouts increases until it reaches 6 with $|\mathcal{T}| = 10$.} We can observe in Figure~\ref{fig:pspace_quality} the opposite behaviour to Figure~\ref{fig:np_quality}; that is, we find a drop of the quality as the input knowledge increases. The drop in the score is caused by the increasing number of timeouts, meaning that no solution is found in many tasks within the given time-bound, and consequently a value of $0$ for precision and recall is assigned to these experiments. Figure \ref{fig:pspace_time}, on the other hand, reflects that the computation time of the first case study is also higher than in the second case, which is explained by both the higher complexity and the large number of timeouts.

### 2018-12-22 doc/aij18/major-revision/letter.tex
Added answers related to section 6 to the letter

@@

\textcolor{red}{FALTA .... }

@@

-          "retain a level of soundness similar to " – what is this "level of soundness"? do you talk about precision?

@@

@@

@@

@@

>>>>

\textcolor{blue}{All plotted values are averages over the 14 (now 15) tested domains. The reviewer is right, however, to point out that this is not said in the experiment of section 6.2, so we have added some lines making it explicit.}

@@

\textcolor{blue}{Timeouts are only observed in the setting with NO action sequences and NO state trajectories. We have added a few sentences providing more details on this issue.}

@@

@@

\textcolor{blue}{Fixed.}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
-          "retain a level of soundness similar to " – what is this "level of soundness"? do you talk about precision?
\end{mdframed}

\textcolor{blue}{Yes, precision gives a notion of soundness since it measures how many of the learned preconditions and effects are correct. We have improved the explanation of the metrics in section 5 to make this more clear.}

@@

\textcolor{blue}{We keep adding new domains as we work on the approach so that number is representative of how many domains we have tested our approach on. We did, however, leave one domain out, {\em Sokoban}. As a matter of fact, this domain has some of the features more difficult to handle for our approach, those are puzzle-like domains and domains with grid-like structure.}

@@

\textcolor{blue}{Predicates with arity 3 are certainly harder but still manageable. In order to proof this, we have added the {\em rovers} domain to the list of domains tested in section 6. }

@@

\textcolor{blue}{Fixed.}
